### 2014-10-24 PrivacyProtection-2014-09-09.tex
finished spec data theft

We follow the Reference Model for IT Security Analyis as described in \cite{Grimm:ItSecRefModel}.
It supersedes earlier efforts by \cite{Avizienis}.

@@

The model is depictured in Figure \ref{fig:refmodel}.
It is organized in four views (round boxes) that contain a number of components (rectangular boxes).

@@

%2. Data Theft
%-------------
%Description: External infiltrates infrastructure in order to steal personal data and sell it on the black market. Also the external might be motivated politically and wants to harm the reputation of the Service Provider or the Local Authority.
%
%COI:         Privacy vs. Financial Profit
%             Reputation of Service Provider vs. Political Activism
%             Reputation of Local Authority vs. Political Activism
%Vuln.:       Insecure Infrastructure, Insecure Communication
%Affected Data:  Data transmitted or stored in data center: GPS trips, HAR-records.
%
%Likeliness: Low-Medium
%Loss: High
%Risk: 4-5
%
\textbf{Data Theft}
Lorem Ipsum

@@

Information given by Comprehension needs to be reliable to found
choices.

>>>>

We follow the Reference Model for IT Security Analysis as described in \cite{Grimm:ItSecRefModel}.
It supersedes earlier efforts by \cite{Avizienis}.

@@

The model is depicted in Figure \ref{fig:refmodel}.
It is organized in four views (round boxes) that contain a number of components (rectangular boxes).

@@

%2. Data Theft
%-------------
%Description: External infiltrates infrastructure in order to steal personal data and sell it on the black market. Also the external might be motivated politically and wants to harm the reputation of the Service Provider or the Local Authority.
%
%COI:         Privacy vs. Financial Profit
%             Reputation of Service Provider vs. Political Activism
%             Reputation of Local Authority vs. Political Activism
%Vuln.:       Insecure Infrastructure, Insecure Communication
%Affected Data:  Data transmitted or stored in data center: GPS trips, HAR-records.
%
%Likeliness: Low-Medium
%Loss: High
%Risk: 4-5
%
\textbf{Data Theft}
An External infiltrates infrastructure in order to steal personal data and sell it on the black market. 
Also the External might be motivated politically and wants to harm the reputation of the System Provider or the Local Authority.
Anyways, this threat would be manifested through a technical attack on either hardware (Packet Capture) or software (buffer overflow, SQL injection).
Such a successful attack could harm the reputation of both System Provider and Local Authority.
The technical competence of System Providers would be proven wrong, therefore they would lose professional reputation.
Local Authorities would lose their political reputation, as it would seem like they had endangered data of Citizens, which lose complete control.
Thus this threat is defined by three conflicts: \textit{Privacy vs. Financial Profit}, \textit{ Reputation of Service Provider vs. Political Activism} and \textit{Reputation of Local Authority vs. Political Activism}.
Also this threat describes the classical scenario, where attacks are provoked by \textit{Insecure Infrastructure} (SQL injection) and \textit{Insecure Communication} (Packet Capture).

@@

Information given by Comprehension needs to be reliable to found
choices.
\end{itemize}
